---
title: "Interactive report for inspecting model outputs"
author: "Ross G. Dwyer, Nils Krueck & Charlie Huveneers"
date: '2022-06-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This DRAFT document presents the preliminary results of modelling work to assess the conservation benefits of no-take marine protected areas (no-take MPAs) to 10 teleost and elasmobranch species based on individual movements and relative abundances. This project is a collaboration between Dr Ross Dwyer (USC), Dr Nils Krueck (UTAS) and Prof Charlie Huveneers (Flinders), with the South Australian Government's Department for Environment and Water as Industry Partners.

The MPA size decision support model was originally developed by Dr Nils Krueck (UTAS) and published here - <https://conbio.onlinelibrary.wiley.com/doi/10.1111/conl.12415>. Dr Ross Dwyer (USC) and Dr Nils Krueck adapted this modelling framework to allow telemetry and BRUV datasets to be included as model inputs. The original paper was published here - <https://www.sciencedirect.com/science/article/pii/S0960982219316008?via%3Dihub>. 

Here, we apply this modelling framework to 6 teleost (Western Blue Groper, Bluethroat Wrasse, Harlequinn, Yellowtail Kingfish, Snapper, Silver Trevally), three shark (Bronze Whaler, Dusky Shark, White Shark) and one ray species (Southern Eagle Ray) to investigate the conservation effectiveness of existing no take reserves in South Australia for these species. 

Effectiveness is measured by: 

* estimated proportion of activity within a no-take MPA
* annual fishing mortality offsets considering variable degrees of fishing morality
* estimated lifetime fishing mortality to longevity under variable degrees of annual fishing morality
* estimated lifetime fishing mortality to age-at-maturity under variable degrees of annual fishing morality
* the total number of individuals protected over their lifetime considering variable degrees of fishing morality


```{r, echo=FALSE,results='hide', message=FALSE, warning=FALSE}
# 1. Load the packages -----------
library(rgdal)
library(rgeos)
library(sp)
library(sf)
library(rmapshaper)
library(magrittr)
library(ggplot2)
library(plotly)
library(tmap)
library(stringr)
library(dplyr)
library(matrixStats)
```

```{r, echo=FALSE}
# Full address of the R Studio Project where data and R code are stored (needed for reproducing markdown report)
maindir <- "/Users/rdwyer2/GitHub/ParksSA/" 
```
First we set the model parameters

```{r, echo=FALSE}
# Set file locations -------
modelid <- 100 # specify model version / id
datadir <- paste0(maindir, 'Data/') 
results.folder <- 'Results/'
modelversion <- paste0("SA_MPAsizer",modelid) # What model version are we using?
resultsdir <- paste0(maindir,results.folder,modelversion,'/') # Where the Results .RDS files are stored
```

```{r}
# Set model parameters -------
case.study.region <- "SA_idealized"
resolution <- 100
dispersal.period <- "Weekly"
age <- "Maturity"
age2 <- "Max"
rBRUVcatchment <- 100
```

```{r, echo=FALSE}
# This is where we set which model we are working with (pulls in the correct returndat folder)
scenario.name <- paste0(case.study.region,'_Res', resolution,'_',dispersal.period,'_AgeAt',age,'_rBRUV',rBRUVcatchment)

returndat <- readRDS(paste0(resultsdir,modelversion,'_',scenario.name,'_returndat.RDS'))

nona.locs <- which(!is.na(returndat)&!is.null(returndat))
returndat <- returndat[nona.locs]
nspecies <- length(returndat)
species.names <- names(returndat) 
SpeciesNames <- str_replace_all(species.names,'_',' ') # Formatted species names

age.data <- read.csv(paste0(datadir,'input_parameters_updated.csv'))
species.groups <- age.data$species.group[match(species.names,age.data$common.name)]
species.order <- order(species.groups,species.names) #species.groups,species.names) # determine order of species to plot
species.names.ordered <- species.names[species.order] # get names of species in order
ngroups <- xtabs(~species.groups)

returndat <- returndat[species.names.ordered]

SpeciesNames <- str_replace_all(species.names.ordered,'_',' ') # Formatted species names

## This bit for the longevity plots

scenario.name2 <- paste0(case.study.region,'_Res', resolution,'_',dispersal.period,'_AgeAt',age2,'_rBRUV',rBRUVcatchment)

returndat2 <- readRDS(paste0(resultsdir,modelversion,'_',scenario.name2,'_returndat.RDS'))

nona.locs <- which(!is.na(returndat2)&!is.null(returndat))
returndat <- returndat[nona.locs]
nspecies <- length(returndat2)
species.names <- names(returndat2) 
SpeciesNames <- str_replace_all(species.names,'_',' ') # Formatted species names

age.data <- read.csv(paste0(datadir,'input_parameters_updated.csv'))
species.groups <- age.data$species.group[match(species.names,age.data$common.name)]
species.order <- order(species.groups,species.names) #species.groups,species.names) # determine order of species to plot
species.names.ordered <- species.names[species.order] # get names of species in order
ngroups <- xtabs(~species.groups)

returndat2 <- returndat2[species.names.ordered]

SpeciesNames <- str_replace_all(species.names.ordered,'_',' ') # Formatted



```


```{r, echo=FALSE}
#Load the plotting functions
source(paste0(maindir,"R Code/Reporting/Plotly MPA functions.R"))
```
Next we calculate the MPA size needed to achieve certain protection levels across the five measures of conservation effectiveness. 

# 1. Time spent in MPAs {.tabset}

## MPAs extending <10 km
```{r, echo=FALSE}
plotPropTim(sxaxis=10,sd=TRUE) # Plot mean protection with x axis <10 km
```

## MPAs extending <100 km
```{r, echo=FALSE}
plotPropTim(sd=TRUE) # Plot mean protection with x axis <100 km
```

# 2. Annual fishing mortality offsets {.tabset}

## F = 0.05
```{r, echo=FALSE}
#foffs.d <- round(foffs,2) # Round to 2 decimal places for easy viewing
plotMortOff(F1="0.05")
```

## F = 0.1
```{r, echo=FALSE}
plotMortOff(F1="0.1")
```

## F = 0.2
```{r, echo=FALSE}
plotMortOff(F1="0.2")
```

## F = 0.5
```{r, echo=FALSE}
plotMortOff(F1="0.5")
```

# 3. Lifetime fishing mortality (to longevity) {.tabset}

## F = 0.05
```{r, echo=FALSE}
plotLifMort_L(F1="0.05",sd=TRUE)
```

## F = 0.1
```{r, echo=FALSE}
plotLifMort_L(F1="0.1",sd=TRUE)
```

## F = 0.2
```{r, echo=FALSE}
plotLifMort_L(F1="0.2",sd=TRUE)
```

## F = 0.5
```{r, echo=FALSE}
plotLifMort_L(F1="0.5",sd=TRUE)
```

# 4. Lifetime fishing mortality (up to age-at-maturity) {.tabset}

## F = 0.05
```{r, echo=FALSE}
plotLifMort(F1="0.05",sd=TRUE)
```

## F = 0.1
```{r, echo=FALSE}
plotLifMort(F1="0.1",sd=TRUE)
```

## F = 0.2
```{r, echo=FALSE}
plotLifMort(F1="0.2",sd=TRUE)
```

## F = 0.5
```{r, echo=FALSE}
plotLifMort(F1="0.5",sd=TRUE)
```


# 5. Number of protected individuals {.tabset}

## F = 0.05
```{r, echo=FALSE}
plotNoInd("0.05")
```

## F = 0.1
```{r, echo=FALSE}
plotNoInd(F1="0.1")
```

## F = 0.2
```{r, echo=FALSE}
plotNoInd(F1="0.2")
```

## F = 0.5
```{r, echo=FALSE}
plotNoInd(F1="0.5")
```


# Mapping South Australia's protected areas {.tabset}

This section displays an interactive map of IUCN Cat II reserves in South Australian Waters. The dataset was sourced from the Australian Government Collaborative Australian Protected Area Database (CAPAD 2020) <https://www.awe.gov.au/agriculture-land/land/nrs/science/capad>. Areas are coloured according to (a) maximum reserve width or (b) the minimum distance between Cat II reserves. 

```{r, echo=FALSE,results='hide', message=FALSE, warning=FALSE}
tmap_mode("view")
SAMPA_CatII_nearest_sf <- readRDS(paste0(maindir,"R Code/Reporting/SAMPA_CatII_nearest.RDS"))
```

## Max width 
```{r, echo=FALSE}
tm_shape(SAMPA_CatII_nearest_sf) + 
  tm_fill("MaxDist_km", 
          title="Maximum width of no-take MPA (km)",
          id="NAME", 
          breaks = c(0,5,10,20,30,50,100,200),
          palette = rev(sf.colors(7)),
          popup.vars=c("Type"="TYPE",
                       "RES_NUMBER"="RES_NUMBER",
                       "Distance to nearest no-take MPA (km)"="Nearest_km", 
                       "Max width (km)"="MaxDist_km", 
                       "Area"="GAZ_AREA"))

```

## Min distance
```{r, echo=FALSE,message=FALSE, warning=FALSE}
tm_shape(SAMPA_CatII_nearest_sf) + 
  tm_fill("Nearest_km", 
          title="Minimum distance between no-take MPAs (km)",
          id="NAME", 
          breaks = c(0,5,10,20,40,60,80),
          palette = sf.colors(7),
          popup.vars=c("Type"="TYPE",
                       "RES_NUMBER"="RES_NUMBER",
                       "Distance to nearest no-take MPA (km)"="Nearest_km", 
                       "Max width (km)"="MaxDist_km", 
                       "Area"="GAZ_AREA"))

```

# {.tabset}
```{r, echo=FALSE,results='hide', message=FALSE, warning=FALSE}
vline <- function(x = 30, color = "black") {
  list(
    type = "line",
    y0 = 0,
    y1 = 1,
    yref = "paper",
    x0 = x,
    x1 = x,
    line = list(color = color)
  )
}
```

## Max width 
```{r, echo=FALSE,message=FALSE, warning=FALSE}
MaxDist_km_mean <- round(mean(SAMPA_CatII_nearest_sf$MaxDist_km),1)
MaxDist_km_median <- round(median(SAMPA_CatII_nearest_sf$MaxDist_km),1)

p1 <- SAMPA_CatII_nearest_sf %>% 
  st_drop_geometry() %>% 
  plot_ly(x = ~MaxDist_km, type = "histogram",
  xbins = list(size = 5)) %>% 
  layout(title = 'Histogram of maximum width of SA no-take MPAs', 
         plot_bgcolor = "#e5ecf6",
         xaxis = list(title = 'Maximum width (km) of no-take MPA'), 
         yaxis = list(title = 'Frequency'),
         shapes = list(
           vline(MaxDist_km_mean),
           vline(MaxDist_km_median,color="orange"))) %>% 
  add_text(showlegend = FALSE, 
           x = c(MaxDist_km_mean+10,MaxDist_km_median+10), 
           y = c(5,3),
           text = c(paste0("mean = ",MaxDist_km_mean," km"),
                    paste0("median = ",MaxDist_km_median," km")),
           textfont = list(color = c('black','orange'), size = c(14,14)))
         
p1
```

## Min distance
```{r, echo=FALSE,message=FALSE, warning=FALSE}
Nearest_km_mean <- round(mean(SAMPA_CatII_nearest_sf$Nearest_km),1)
Nearest_km_median <- round(median(SAMPA_CatII_nearest_sf$Nearest_km),1)

p2 <- SAMPA_CatII_nearest_sf %>% 
  st_drop_geometry() %>% 
  plot_ly(x = ~Nearest_km, type = "histogram",
  xbins = list(size = 5)) %>% 
  layout(title = 'Histogram of minimum distance between SA no-take MPAs', 
         plot_bgcolor = "#e5ecf6",
         xaxis = list(title = 'Minimum distance (km) between no-take MPAs'), 
         yaxis = list(title = 'Frequency'),
         shapes = list(
           vline(Nearest_km_mean),
           vline(Nearest_km_median,color="orange"))) %>% 
  add_text(showlegend = FALSE, 
           x = c(Nearest_km_mean,Nearest_km_median), 
           y = c(5,3),
           text = c(paste0("mean = ",Nearest_km_mean," km"),
                    paste0("median = ",Nearest_km_median," km")),
           textfont = list(color = c('black','orange'), size = c(14,14)))
         
p2
```
